---
title: "Class enrollment Data:MA132"
author: "Andrew Stephens"
Date: "21 Sep 2020"
output: html_notebook
---

The intention of this analysis is to use past enrollment data to predict total enrollment in MA132. 


Prepare workspace:

## Load Packages
```{r}
library(tidyverse)
library(janitor)
library(readxl)
library(skimr)
library(summarytools)

```


## Read and clean the data

```{r}
dfa = read_excel("~/DS241/CU_ACAD_DEPT_ENRL (1).xlsx") %>%
  clean_names()
```

```{r}
skim(dfa)
```

### Tidy data

Let's separate column term2 into two variables.

```{r}
dfb = dfa %>% separate(col=term2, into=c("semester", "year"), sep=" ")
```

### Clean and subset the data

We get rid of the following variables:

* acad_org
* current_status
* instructor
* course_id

Filtering to only include:

* math courses
* catalog numbers for MA131 and 132
* lectures

Use distinct to remove duplicate rows

Summarize enrollment

```{r}
dfc=dfb %>% select(-acad_org,-current_status,-instructor,-course_id)%>%
  filter(subject=="MA") %>%
  filter(catalog %in% c("131","132")) %>%
  filter(component=="LEC") %>%
  distinct() %>%
  group_by(catalog,semester,year) %>%
  summarise(combined_tot_enrl=sum(tot_enrl))
  
```



